% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2011-2012 Geniusy <geniusy.jiang@gmail.com>
% http://www.geniusy.com
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage[hidelinks]{hyperref}
\usepackage[top=0.5in, bottom=0.1in, left=1in, right=1in]{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}


% Set your name here
\def\name{Lei Cao}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
% \def\footerlink{http://www.geniusy.com/jiangbo-cv.pdf}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

%\geometry{
%  body={6.5in, 9in},
%  left=1.0in,
%  top=0.8in
%}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
\begin{list}{*}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0pt}
  }
}{
  \end{list}
}

%\let\oldenumerate\enumerate
%\renewcommand{\enumerate}{
%	\oldenumerate
%	\setlength{\leftmargin}{1.5em}
%	\setlength{\itemsep}{0pt}
%}

\renewcommand\arraystretch{1.35}

\begin{document}

% Place name at left
% {\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\begin{minipage}{0.55\linewidth}
  {\huge \name}
\end{minipage}
\begin{minipage}{0.40\linewidth}
  Phone: ($+$86) 139-6710-4554 \\
  Email: \href{mailto:jslhcl@gmail.com}{\tt jslhcl@gmail.com} \\
  Github: \url{https://github.com/jslhcl/} 
\end{minipage}

\rule{16.8cm}{0.1em}

\vspace{-1em}
\section*{Work \& Project Experience}

\subsection*{\textbf{Microsoft, 2015.8 - Present:\hfill SDE II}}
Work in SharePoint team to implement and maintain this web application platform with C\#
\begin{itemize}
\item Lead SharePoint Hybrid team on various Hybrid feature design and implementation to contribute more SPO MAU.
\item Designed and implemented a tool to migrate files from local file system and SharePoint onPrem libraries to SharePoint Online, to provide stable service for huge data with good performance
\item Created an internal website on top of SharePoint with jQuery
\item Implemented app launcher in SharePoint 2013 for users to quickly access different sites with C\#, JavaScript and CSS.
\item Designed and implemented dashboards to monitor the usage of SharePoint features of our team by quering from Cosmos (Microsoft's BigData analysis platform)
\end{itemize}
%
\subsection*{\textbf{MicroStrategy, 2010.8 - 2015.7:\hfill Principal Software Engineer}}
Key programmer on the infrastructure team of the company:
\begin{itemize}
\item Migrated SCM tool from ClearCase to Git. Customize Git for multi-repo management(\href{https://source.android.com/source/using-repo.html}{google-repo}) and binary optimization(\href{https://github.com/cyaninc/git-fat}{git-fat}), contributed issues fixing for the open source migrating tool(\href{https://github.com/charleso/git-cc/issues/57}{git-cc}) 
\end{itemize}
Key programmer on the Business Intelligence software for data analysis and visualization on multiple platforms:
\begin{itemize}
\item \href{http://www.microstrategy.com/us/analytics/desktop}{\textbf{MicroStrategy Desktop}} in Windows and Mac version, which is a desktop app for data analysis and visualization using \href{https://bitbucket.org/chromiumembedded/cef}{CEF}/UIWebView from multiple data source(local file/database/Internet/our server). Worked on almost all aspects of this product and Fixed several critical crash in release build/specific machine/multiple users case.
\item \href{http://www.microstrategy.com/us/analytics}{\textbf{MicroStrategy}} in HTML5 version. Key designer and programmer on server side, which generates JSON and provides REST-like API for clients. Made big progress in program stability and performance (JSON size is reduced by 15\%).
\item \href{http://www.microstrategy.com/us/mobile}{\textbf{MicroStrategy Mobile}} in iOS \& Android app. Client side programmer on the cross-platform C/C++ code (accessed by Objective-C and JNI respectively), to provide platform \& backward compatibility, as well as consistent user experience, and support all kinds of user manipulations. Also some GUI feature such as \href{https://developers.facebook.com/docs/facebook-login/ios/}{Facebook Native login} to make the login process faster and safer.
\end{itemize}

\rule{16.8cm}{0.1em}

%\vspace{-1.5em}
\vspace{-1em}
\section*{Education}
\begin{itemize}
	\item \textbf{Peking University}, M.S. Application of Computer Software, 2007-2010.
	\item \textbf{Nanjing University}, Bachelor (GPA 4.36/5). Computer Science \& Technology, 2003-2007.
\end{itemize}

\rule{16.8cm}{0.1em}

%\vspace{-1.5em}
\vspace{-1em}
\section*{Personal Skills}
\begin{itemize}
\item \textbf{Language}: (experienced) C/C++, C\#, Matlab; (Good) Java, Python, Objective-C, JavaScript, \LaTeX, C++/CLI, ActionScript
\item \textbf{Linux} user since 2007, familiar with common tools such as Bash, AWK, Sed, etc
\end{itemize}

\rule{16.8cm}{0.1em}

%\vspace{-1.5em}
\vspace{-1em}
\section*{Awards}
\begin{itemize}
\item Finalist in 2013 MicroStrategy Hackathon, 2013.12
\item Rookie Of the Year (best of the new hires of the year), MicroStrategy Inc., 2012.1
\item Second Place in TRECVID 2009 (an International video retrieval contest), 2009.10
\end{itemize}

\end{document}
